Supplementary Material for Food-web complexity alters the fitness landscape

### 2018-06-21 supp_mat_complexity_selection.Rmd
removed cached files to be able to push commit. I think I can avoid this if I simply split up the chunks into Relative and Absolute fitness.
Former-commit-id: 2d5ce108463a82db67374a2a6afd5d8431c597e2

# Format plots
RF_landscape_plots <- plot_grid(
  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
  RF_plot_size.x.preference + theme(legend.position = "none"), 
  nrow=2, align="hv", labels = "AUTO")
RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
RF_landscape_2d
#save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
#save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)

@@

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
  AF_plot_size.x.preference + theme(legend.position = "none"), 
  nrow=2, align="hv", labels = "AUTO")
AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
AF_landscape_2d
#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
#save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
```

>>>>

# Format plots
RF_landscape_plots <- plot_grid(
  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
  RF_plot_size.x.preference + theme(legend.position = "none"), 
  nrow=2, align="hv", labels = "AUTO")
RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
#RF_landscape_2d
#save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
#save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)

@@

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
  AF_plot_size.x.preference + theme(legend.position = "none"), 
  nrow=2, align="hv", labels = "AUTO")
AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
#AF_landscape_2d
#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
#save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
```
